Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
write on S_1 x

The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training a classifier.

>>>>

The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training the classifier.
From any set of descriptors, \eg a time-frequency representation $\boldsymbol{x_1}(t,\gamma_1)$,
a translation-invariant representation up to time skills of duration $T$ can be simply obtained
by concolving $\boldsymbol{x_1}$ with a low-pass filter $\boldsymbol{\phi}(t)$ of cutoff frequency
set to $1/T$:
\begin{equation}
\mathbf{S_1}\boldsymbol{x}(t, \gamma_1) = (\boldsymbol{x_1} \ast \phi) (t).
\end{equation}
